---
title: "R Markdown Presentation and Plotly"
author: "Anna Teplukhina"
date: "13 July 2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This project is dedicated to creating a web page presentation using R Markdown that features an interactive plot created by the Plotly package.

On the next slides one can see the R Markdown code to create an interactive plot with the data set `ToothGrowth` and the plot itself. This data set shows the effect of vitamin C on tooth growth in guinea pigs. 

## Generating the plot
First, one should load the `plotly` library:
```{r, echo=TRUE, warning=FALSE, message=FALSE}
library(plotly)
```

Now, one can load the data set `ToothGrowth` and creat a box plot. There are three main characteristics: the observation length `len`, supplement type `supp` (OJ and VC), and the dose level `dose` fixed at 0.5, 1.0 and 2.0 mg level.
```{r, echo=TRUE, eval=FALSE}
data(ToothGrowth)
plot_ly(ToothGrowth, x = ~dose, y = ~len, color=~supp, type = "box")
```

## The box plot
```{r, warning=FALSE, message=FALSE}
data(ToothGrowth)
plot_ly(ToothGrowth, x = ~dose, y = ~len, color=~supp, type = "box")
```


